\hspace{1cm} Do syntactic and semantic similarity lead to interference effects? \newline Evidence from self-paced reading and event-related potentials using German

### 2024-08-26 paper/main.tex
Updated via the Open Science Framework

\subsection{Discussion}
We presented the to-date largest-sample self-paced reading study that investigated the use of syntactic and semantic features during subject-verb dependency formation. \textcolor{blue}{The reading time results at the critical verb showed anecdotal evidence against or moderate evidence for semantic interference (BF$_{10}$ between 0.7 and 3.5 depending on a priori assumed effect size), but an effect of semantic interference was present at the regions surrounding the critical verb, i.e., the pre-critical and spill-over region. This means that semantic interference occurred even before the retrieval event could begin. Reading times of the pre-critical word and critical verb showed evidence against syntactic interference. In the spill-over region, there was weak evidence for a small syntactic interference effect in the size of up to $\pm$8 ms. Reading times at the critical verb showed very weak support for a small interaction of syntactic and semantic interference. There was evidence against the interaction under wider priors and in the surrounding regions.} \Copy{only_precritical}{\textcolor{blue}{Given the pre-critical reading times differences, effects in the later regions, i.e., the critical and spill-over region, cannot be attributed clearly to the stimuli in these regions and sentence processing mechanisms associated with them. This means that although it is interesting that small effects of syntactic interference and the interaction emerged only in these regions  any interpretation of these effects would be purely speculative. Therefore, we refrain from discussing the effects occurring in the critical and spill-over regions.}}\label{only_precritical} \textcolor{blue}{We will discuss the absence of decisive evidence for syntactic interference in our data in the general discussion.} The effects in the pre-critical region are discussed next.

>>>>

\subsection{Discussion}
We presented the to-date largest-sample self-paced reading study that investigated the use of syntactic and semantic features during subject-verb dependency formation. \textcolor{blue}{The reading time results at the critical verb showed anecdotal evidence against or moderate evidence for semantic interference (BF$_{10}$ between 0.7 and 3.5 depending on a priori assumed effect size), but an effect of semantic interference was present at the regions surrounding the critical verb, i.e., the pre-critical and spill-over region. This means that semantic interference occurred even before the retrieval event could begin. Reading times of the pre-critical word and critical verb showed evidence against syntactic interference. In the spill-over region, there was weak evidence for a small syntactic interference effect in the size of up to $\pm$8 ms. Reading times at the critical verb showed inconclusive results (neither support for nor against) regarding a very small interaction of syntactic and semantic interference. There was evidence against the interaction under wider priors and in the surrounding regions.} \Copy{only_precritical}{\textcolor{blue}{Given the pre-critical reading time differences, effects in the later regions, i.e., the critical and spill-over region, cannot be attributed clearly to the stimuli in these regions and sentence processing mechanisms associated with them. This means that although it is interesting that a small effect of syntactic interference emerged in the spill-over region any interpretation of this effect would be purely speculative. Therefore, we do not think that this effect can be clearly attributed to retrieval interference due to syntactic similarity and refrain from further discussing this effect occurring in the spill-over region.}}\label{only_precritical} \textcolor{blue}{We will discuss the absence of decisive evidence for syntactic interference in our data in the general discussion.} The effects in the pre-critical region are discussed next.
